---
title: "Thesis_INDUS_Analysis"
format: html
execute:
  warning: false
---
## Explanation

In this document/code, I will examine key dimensions of manafacturing firms. The main goal is to see whether there are differences in key dimensions across different regions. The main characteristics that I will examine are:

1. Firm size (Number of employees)
  i) 2540: (A26 + A31)
  ii) 2550: (A24 + A28)
  iii) 2560: (B04 + B08)
2. Foreign Investment
  i) 2540: A05
  ii) 2550: A09
  iii) 2560: A09
3. Exporting
  i) 2540: A11
  ii) 2550: A15
  iii) 2560: A12
4. Sales
  i) 2540: F01
  ii) 2550: G01
  iii) 2560: D01
5. Profit before tax (Total income - Cost of sales - Administrative expenses - Costs of raw materials, production, goods, work done by others - wages bill)
  i) 2540: F09 - E01 - E02 - C01 - C02 - C03 - C04 - B04 - B08 - B09 - B10 - B11
  ii) 2550: G01 + G13 - E01 - E02 - C01 - C02 - C03 - C04 - B05 - B10
  iii) 2560: D01 + D13 - C21 - C41 - C06 - B19 - B24
6. Total Fixed Assets
  i) 2540: H07
  ii) 2550: I08
  iii) 2560:
7. Problems of operation
  i) 2560: J02, J03, J04, J05, J06, J07, J08, J09, J10, J11, J12, J13, J14, J15, J16, J17
  --> Group into:
  a) Low Demand or Marketing Problems: J02, J10, J11
  b) Labor Shortages: J05
  c) Lack of capital: J09
  d) Technology Problem: J06, J07
8. Needs from the government
  i) 2560: J19, J20, J21, J22, J23, J24, J25, J26, J27, J28, J29, J30, J31, J32, J33, J34
  --> Group into:
  a) Skilled_Labor_support: J19
  b) Productivity_support: J20, J32
  c) Capital_Support: J21, J22, J23, J32
  d) Output_Market_Support: J25, J30
9. R&D Costs
  i) 2540: No info
  ii) 2550: E28
  iii) 2560: C32
10. Number of firms
  i) 2540: ??
  ii) 2550: sum of weights
  iii) 2560: sum of weights
11. Estimated TFP (estimated using sales, wage bill, and fixed assets).
12. Value-added/Employee: Value added is calculated as sales - cost of raw materials + change in inventory of raw materials.
  i) 2550: (G01 + (D05 - D01) - C01)/(A24 + A28)
  ii) 2560: (D01 + (C12 – C07) – C01)/(B04 + B08)
13. K/L
  i) 2550: I08/(A24 + A28)
  ii) 2560: E16/(B04 + B08)



## Import and Clean Data
```{r}
remove(list = ls())

library(readxl)
library(dplyr)
library(ggplot2)
library(tidyr)
library(haven)
library(ggstats)
library(lemon)
library(kableExtra)
library(mmtable2)
library(stringr)
library(purrr)
library(gt)
library(gapminder)

# Set working directory
setwd("D:/Onedrive-CEU/OneDrive - Central European University/CEU/Thesis/Thesis_code")

# Importing the data
INDUS_2540 <- read_sav("Data\\INDUS 2540 (1997)\\Microdata INDUS 2540\\Microdata INDUS 2540.sav")

INDUS_2550 <- read_sav("Data\\INDUS 2550 (2007)\\Microdata INDUS 2550\\Microdata INDUS 2550.sav")

INDUS_2560 <- read_sav("Data\\INDUS 2560 (2018)\\Microdata INDUS 2560\\Microdata INDUS 2560.sav")

LFS_LF <- read_excel("Data/Output/All_YEAR_TOTAL_LF_annual_final.xlsx")


```

# Analysis of all firms

## Pre-processing the data
### Divide weight by 10,000
```{r}
INDUS_2550 <- INDUS_2550 %>% mutate(WGT_CWT = WGT_CWT/10000, WGT_REG = WGT_REG/10000)

```

## Group the needs from the government

```{r}
## First, turn missing values into 0
INDUS_2560 <- INDUS_2560 %>% mutate(J19 = ifelse(is.na(J19), 0, J19), J20 = ifelse(is.na(J20), 0, J20), J21 = ifelse(is.na(J21), 0, J21), J22 = ifelse(is.na(J22), 0, J22), J23 = ifelse(is.na(J23), 0, J23), J24 = ifelse(is.na(J24), 0, J24), J25 = ifelse(is.na(J25), 0, J25), J26 = ifelse(is.na(J26), 0, J26), J27 = ifelse(is.na(J27), 0, J27), J28 = ifelse(is.na(J28), 0, J28), J29 = ifelse(is.na(J29), 0, J29), J30 = ifelse(is.na(J30), 0, J30), J31 = ifelse(is.na(J31), 0, J31), J32 = ifelse(is.na(J32), 0, J32), J33 = ifelse(is.na(J33), 0, J33), J34 = ifelse(is.na(J34), 0, J34))

## Group the needs from the government (4 groups)
INDUS_2560 <- INDUS_2560 %>% mutate(Skilled_Labor_support = J19, Productivity_support = J20 + J32, Capital_Support = J21 + J22 + J23 + J32, Output_Market_Support = J25 + J30)

# If > 0 then 1, else 0
INDUS_2560 <- INDUS_2560 %>% mutate(Skilled_Labor_support = ifelse(Skilled_Labor_support > 0, 1, 0), Productivity_support = ifelse(Productivity_support > 0, 1, 0), Capital_Support = ifelse(Capital_Support > 0, 1, 0), Output_Market_Support = ifelse(Output_Market_Support > 0, 1, 0))


```

## Group the problems of operation

```{r}
## First, turn missing values into 0
INDUS_2560 <- INDUS_2560 %>% mutate(J02 = ifelse(is.na(J02), 0, J02), J03 = ifelse(is.na(J03), 0, J03), J04 = ifelse(is.na(J04), 0, J04), J05 = ifelse(is.na(J05), 0, J05), J06 = ifelse(is.na(J06), 0, J06), J07 = ifelse(is.na(J07), 0, J07), J08 = ifelse(is.na(J08), 0, J08), J09 = ifelse(is.na(J09), 0, J09), J10 = ifelse(is.na(J10), 0, J10), J11 = ifelse(is.na(J11), 0, J11), J12 = ifelse(is.na(J12), 0, J12), J13 = ifelse(is.na(J13), 0, J13), J14 = ifelse(is.na(J14), 0, J14), J15 = ifelse(is.na(J15), 0, J15), J16 = ifelse(is.na(J16), 0, J16), J17 = ifelse(is.na(J17), 0, J17))

## Group the problems of operation (4 groups)
INDUS_2560 <- INDUS_2560 %>% mutate(Low_Demand_Marketing_Problems = J02 + J10 + J11, Labor_Shortages = J05, Lack_of_Capital = J09, Technology_Problem = J06 + J07)

# If > 0 then 1, else 0
INDUS_2560 <- INDUS_2560 %>% mutate(Low_Demand_Marketing_Problems = ifelse(Low_Demand_Marketing_Problems > 0, 1, 0), Labor_Shortages = ifelse(Labor_Shortages > 0, 1, 0), Lack_of_Capital = ifelse(Lack_of_Capital > 0, 1, 0), Technology_Problem = ifelse(Technology_Problem > 0, 1, 0))

```


## Calculate value-added per employee

```{r}
## Using only firms with sales > 12.000
# 2550. (G01 + (D05 - D01) - C01)/(A24 + A28)
INDUS_2550_VA_filtered <- INDUS_2550 %>% filter(G01 > 12000, !is.na(G01), !is.na(D05), !is.na(D01), !is.na(C01))
# If A24, A28 = NA then replace with 0
INDUS_2550_VA_filtered <- INDUS_2550_VA_filtered %>% mutate(A24 = ifelse(is.na(A24), 0, A24), A28 = ifelse(is.na(A28), 0, A28))
# Calculate value-added.
INDUS_2550_VA_filtered <- INDUS_2550_VA_filtered %>% mutate(Value_Added = (G01 + (D05 - D01) - C01))
# Calculate value-added per employee.
INDUS_2550_VA_filtered <- INDUS_2550_VA_filtered %>% mutate(Value_Added_per_emp = Value_Added/(A24 + A28))

# 2560. (D01 + (C12 – C07) – C01)/(B04 + B08)
INDUS_2560_VA_filtered <- INDUS_2560 %>% filter(D01 > 12000, !is.na(D01), !is.na(C12), !is.na(C07), !is.na(C01))
# If B04, B08 = NA then replace with 0
INDUS_2560_VA_filtered <- INDUS_2560_VA_filtered %>% mutate(B04 = ifelse(is.na(B04), 0, B04), B08 = ifelse(is.na(B08), 0, B08))
# Calculate value-added.
INDUS_2560_VA_filtered <- INDUS_2560_VA_filtered %>% mutate(Value_Added = (D01 + (C12 - C07) - C01))
# Calculate value-added per employee.
INDUS_2560_VA_filtered <- INDUS_2560_VA_filtered %>% mutate(Value_Added_per_emp = Value_Added/(B04 + B08))
```


## Calculate K/L

```{r}
## Using only firms with sales > 12.000, and fixed assets > 6,000.
# 2550. I08/(A24 + A28)
INDUS_2550_KL_filtered <- INDUS_2550 %>% filter(G01 > 12000, I08 > 6000, !is.na(G01), !is.na(I08), !is.na(A24), !is.na(A28))
# Replace missing A24, A28 with 0
INDUS_2550_KL_filtered <- INDUS_2550_KL_filtered %>% mutate(A24 = ifelse(is.na(A24), 0, A24), A28 = ifelse(is.na(A28), 0, A28))

# Calculate K/L
INDUS_2550_KL_filtered <- INDUS_2550_KL_filtered %>% mutate(Capital_to_Labor = I08/(A24 + A28))

# 2560. E16/(B04 + B08)
INDUS_2560_KL_filtered <- INDUS_2560 %>% filter(D01 > 12000, E16 > 6000, !is.na(D01), !is.na(E16), !is.na(B04), !is.na(B08))
# Replace missing B04, B08 with 0
INDUS_2560_KL_filtered <- INDUS_2560_KL_filtered %>% mutate(B04 = ifelse(is.na(B04), 0, B04), B08 = ifelse(is.na(B08), 0, B08))

# Calculate K/L
INDUS_2560_KL_filtered <- INDUS_2560_KL_filtered %>% mutate(Capital_to_Labor = E16/(B04 + B08))
```


### Categorize number of employees (follow the same categorization as in year 2550)
1. 1
2. 2-3
3. 4-5
4. 6-10
5. 11-15
6. 16-20
7. 21-25
8. 26-30
9. 31-50
10. 51-100
11. 101-200
12. 201-500
13. 501-1000
14. > 1000

```{r}
## Categorized number of employees (2560)\
# 1 + NA should be 1
INDUS_2560 <- INDUS_2560 %>% mutate(B04 = ifelse(is.na(B04), 0, B04), B08 = ifelse(is.na(B08), 0, B08)) %>% mutate(SIZE_R = case_when(B04 + B08 == 1 ~ 1, B04 + B08 >= 2 & B04 + B08 <= 3 ~ 2, B04 + B08 >= 4 & B04 + B08 <= 5 ~ 3, B04 + B08 >= 6 & B04 + B08 <= 10 ~ 4, B04 + B08 >= 11 & B04 + B08 <= 15 ~ 5, B04 + B08 >= 16 & B04 + B08 <= 20 ~ 6, B04 + B08 >= 21 & B04 + B08 <= 25 ~ 7, B04 + B08 >= 26 & B04 + B08 <= 30 ~ 8, B04 + B08 >= 31 & B04 + B08 <= 50 ~ 9, B04 + B08 >= 51 & B04 + B08 <= 100 ~ 10, B04 + B08 >= 101 & B04 + B08 <= 200 ~ 11, B04 + B08 >= 201 & B04 + B08 <= 500 ~ 12, B04 + B08 >= 501 & B04 + B08 <= 1000 ~ 13, B04 + B08 > 1000 ~ 14))

```



```{r}
## Convert SIZE_R to factor
INDUS_2550 <- INDUS_2550 %>% mutate(SIZE_R = factor(SIZE_R, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14), labels = c("1", "2-3", "4-5", "6-10", "11-15", "16-20", "21-25", "26-30", "31-50", "51-100", "101-200", "201-500", "501-1000", ">1000")))

INDUS_2560 <- INDUS_2560 %>% mutate(SIZE_R = factor(SIZE_R, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14), labels = c("1", "2-3", "4-5", "6-10", "11-15", "16-20", "21-25", "26-30", "31-50", "51-100", "101-200", "201-500", "501-1000", ">1000")))


```



## Tabulating the data
### Firm Size (by region)

```{r}
### Calculate the average number of employees by region
# 2550
Avg_emp_2550 <- INDUS_2550 %>% mutate(A24 = ifelse(is.na(A24), 0, A24), A28 = ifelse(is.na(A28), 0, A28)) %>% group_by(REG) %>% summarise(Avg_emp_50 = weighted.mean(A24 + A28, WGT_REG, na.rm = TRUE))

# 2560
Avg_emp_2560 <- INDUS_2560 %>% mutate(B04 = ifelse(is.na(B04), 0, B04), B08 = ifelse(is.na(B08), 0, B08)) %>% group_by(REG) %>% summarise(Avg_emp_60 = weighted.mean(B04 + B08, WGT, na.rm = TRUE))

```

### Number of firms (by region)

```{r}
# 2550
Num_firms_2550 <- INDUS_2550 %>% group_by(REG) %>% summarise(Num_firms_50 = sum(WGT_REG, na.rm = TRUE))

# 2560
Num_firms_2560 <- INDUS_2560 %>% group_by(REG) %>% summarise(Num_firms_60 = sum(WGT, na.rm = TRUE))
```


#### Compare with the labor force.

```{r}
### Join the three tables (Average number of employees, Number of firms, and labor force)
## 2549
Emp_Num_LF_2549 <- Avg_emp_2550 %>% left_join(Num_firms_2550, by = "REG")

# Join with the labor force
Emp_Num_LF_2549 <- Emp_Num_LF_2549 %>% left_join(LFS_LF %>% filter(Year == 2549), by = c("REG" = "reg"))

# Divide the labor force by 10,000
Emp_Num_LF_2549 <- Emp_Num_LF_2549 %>% mutate(wgt = wgt/10000)


#Rename the columns
Emp_Num_LF_2549 <- Emp_Num_LF_2549 %>% rename(Avg_emp = Avg_emp_50, Num_firms = Num_firms_50, Labor_Force = wgt)

## 2559
Emp_Num_LF_2559 <- Avg_emp_2560 %>% left_join(Num_firms_2560, by = "REG")

# Join with the labor force
Emp_Num_LF_2559 <- Emp_Num_LF_2559 %>% left_join(LFS_LF %>% filter(Year == 2559), by = c("REG" = "reg"))


#Rename the columns
Emp_Num_LF_2559 <- Emp_Num_LF_2559 %>% rename(Avg_emp = Avg_emp_60, Num_firms = Num_firms_60, Labor_Force = wgt)

## Concatenate the two tables
Emp_Num_LF <- rbind(Emp_Num_LF_2549, Emp_Num_LF_2559)

## Convert year to C.E.
Emp_Num_LF$Year <- Emp_Num_LF$Year - 543

### Make another dataframe where the number of firms is divided by 10,000 and the labor force is divided by 1,000,000
Emp_Num_LF_scaled <- Emp_Num_LF %>% mutate(Num_firms = Num_firms/10000, Labor_Force = Labor_Force/1000000)

```


### Needs from the government

```{r}
## Calculate the proportion of firms that need support from the government in each category by region.
# 2560
Needs_2560 <- INDUS_2560 %>% group_by(REG) %>% summarise(Skilled_Labor_support = weighted.mean(Skilled_Labor_support, WGT, na.rm = TRUE), Productivity_support = weighted.mean(Productivity_support, WGT, na.rm = TRUE), Capital_Support = weighted.mean(Capital_Support, WGT, na.rm = TRUE), Output_Market_Support = weighted.mean(Output_Market_Support, WGT, na.rm = TRUE))



```


### Problems of operation

```{r}
## Calculate the proportion of firms that face problems of operation in each category by region.
# 2560
Problems_2560 <- INDUS_2560 %>% group_by(REG) %>% summarise(Low_Demand_Marketing_Problems = weighted.mean(Low_Demand_Marketing_Problems, WGT, na.rm = TRUE), Labor_Shortages = weighted.mean(Labor_Shortages, WGT, na.rm = TRUE), Lack_of_Capital = weighted.mean(Lack_of_Capital, WGT, na.rm = TRUE), Technology_Problem = weighted.mean(Technology_Problem, WGT, na.rm = TRUE))

```


### K/L

```{r}
### Calculate average K/L by region.
# 2550
Capital_to_Labor_2550 <- INDUS_2550_KL_filtered %>% group_by(REG) %>% summarise(Avg_Capital_to_Labor = weighted.mean(Capital_to_Labor, WGT_REG, na.rm = TRUE))

# 2560
Capital_to_Labor_2560 <- INDUS_2560_KL_filtered %>% group_by(REG) %>% summarise(Avg_Capital_to_Labor = weighted.mean(Capital_to_Labor, WGT, na.rm = TRUE))

```

### Value-added per employee

```{r}
### Calculate average value-added per employee by region.
# 2550
Value_Added_per_emp_2550 <- INDUS_2550_VA_filtered %>% group_by(REG) %>% summarise(Avg_Value_Added_per_emp = weighted.mean(Value_Added_per_emp, WGT_REG, na.rm = TRUE))

# 2560
Value_Added_per_emp_2560 <- INDUS_2560_VA_filtered %>% group_by(REG) %>% summarise(Avg_Value_Added_per_emp = weighted.mean(Value_Added_per_emp, WGT, na.rm = TRUE))
```

## Combine to make two main tables.
### Number of firms, average number of employees, and labor force

```{r}
# Change region to actual names
Emp_Num_LF_scaled <- Emp_Num_LF_scaled %>% mutate(REG = case_when(REG == "1" ~ "Bangkok", REG == "2" ~ "Central", REG == "3" ~ "North", REG == "4" ~ "Northeast", REG == "5" ~ "South"))

```

```{r}
## Let's try creating the table with gt.
Emp_Num_LF_scaled %>% gt(rowname_col = "REG", groupname_col = "Year") %>% cols_label(Avg_emp = "Average number of employees", Num_firms = "Number of firms (10,000)", Labor_Force = "Labor force (millions)") %>% cols_align(align = "center") %>% cols_width(everything() ~ px(160)) %>% fmt_number(decimals = 2)
  

```


### K/L and Value-added per employee

```{r}
### Combine K/L of two years
# First, add year to the tables
Capital_to_Labor_2550 <- Capital_to_Labor_2550 %>% mutate(Year = 2006)
Capital_to_Labor_2560 <- Capital_to_Labor_2560 %>% mutate(Year = 2016)

# Concatenate the two tables
Capital_to_Labor <- rbind(Capital_to_Labor_2550, Capital_to_Labor_2560)

```

```{r}
### Combine value-added per employee of two years
# First, add year to the tables
Value_Added_per_emp_2550 <- Value_Added_per_emp_2550 %>% mutate(Year = 2006)
Value_Added_per_emp_2560 <- Value_Added_per_emp_2560 %>% mutate(Year = 2016)

# Concatenate the two tables
Value_Added_per_emp <- rbind(Value_Added_per_emp_2550, Value_Added_per_emp_2560)

```

```{r}
## Combine the two tables
KLVAPerEmp <- Capital_to_Labor %>% left_join(Value_Added_per_emp, by = c("REG", "Year"))

```


```{r}
### Make nice table 
# Change region to actual names
KLVAPerEmp <- KLVAPerEmp %>% mutate(REG = case_when(REG == "1" ~ "Bangkok", REG == "2" ~ "Central", REG == "3" ~ "North", REG == "4" ~ "Northeast", REG == "5" ~ "South"))
```


```{r}
## Let's try creating the table with gt.
KLVAPerEmp %>% gt(rowname_col = "REG", groupname_col = "Year") %>% cols_label(Avg_Capital_to_Labor = "Average K/L", Avg_Value_Added_per_emp = "Average Value-added per employee") %>% cols_align(align = "center") %>% cols_width(everything() ~ px(160)) %>% fmt_number(decimals = 0)
  

```


## Plotting the data

```{r}
## Make a region labeller.
region_labeller <- as_labeller(c( "0" = "National",
  "1" = "Bangkok",
  "2" = "Central",
  "3" = "North",
  "4" = "Northeast",
  "5" = "South"
))
```


### Distribution of Firm Size (by region)

```{r}
# 2550
ggplot(INDUS_2550 %>% drop_na(SIZE_R)) + aes(x = SIZE_R, weight = WGT_REG, y = after_stat(prop)) + geom_bar(stat = "prop") + facet_rep_wrap(~REG, labeller = region_labeller, ncol = 1) + labs(title = "Distribution of Firm Size (by region)", x = "Number of Employees", y = "Proportion")
```


```{r}

# 2560
ggplot(INDUS_2560 %>% drop_na(SIZE_R)) + aes(x = SIZE_R, weight = WGT, y = after_stat(prop)) + geom_bar(stat = "prop") + facet_rep_wrap(~REG, labeller = region_labeller, ncol = 1) + labs(title = "Distribution of Firm Size (by region)", x = "Number of Employees", y = "Proportion")


```

```{r}
## Overlay the two graphs
Dist_overlay <- ggplot(NULL, aes(x = SIZE_R, y = after_stat(prop))) + geom_bar(data = INDUS_2550 %>% drop_na(SIZE_R), aes(weight = WGT_REG, fill = "2006"), stat = "prop", alpha = 0.4) + geom_bar(data = INDUS_2560 %>% drop_na(SIZE_R), aes(weight = WGT, fill = "2016"), stat = "prop", alpha = 0.4) + facet_rep_wrap(~REG, labeller = region_labeller, ncol = 1) + labs(title = "Distribution of Firm Size (by region)", x = "Number of Employees", y = "Proportion") + labs(fill = "Year") + theme(legend.position = "bottom")


Dist_overlay


```

### Number of firms, average number of employees, and labor force (by region)

```{r}
### Grouped bar chart. Each region is a facet.
# Make year as discrete
Emp_Num_LF_scaled$Year <- as.factor(Emp_Num_LF_scaled$Year)

## Convert the data to long format
Emp_Num_LF_long <- Emp_Num_LF_scaled %>% pivot_longer(cols = c("Avg_emp", "Num_firms", "Labor_Force"), names_to = "Variable", values_to = "Value")

# Order in each group.
Emp_Num_LF_long$Variable <- factor(Emp_Num_LF_long$Variable, levels = c("Avg_emp", "Num_firms", "Labor_Force"))


# Plot
ggplot(Emp_Num_LF_long) + aes(x = Year, y = Value, fill = Variable) + geom_col(position = "dodge") + facet_wrap(~REG, labeller = region_labeller, ncol = 2) + labs(title = "Number of firms, average number of employees, and labor force (by region)", x = "Year", y = "Value") + theme(legend.position = "bottom") + scale_fill_manual(values = c("blue", "red", "green"), labels = c("Average number of employees", "Number of firms (10,000)", "Labor force (millions)")) + theme(legend.position = "bottom", legend.title = element_blank())


```


### Distribution of value-added per employee (by region)

```{r}
## Check how many have negative value-added per employee
sum(INDUS_2550_VA_filtered$Value_Added_per_emp < 0)
```


```{r}
# 2550
# Make REG as character
INDUS_2550_VA_filtered$REG <- as.character(INDUS_2550_VA_filtered$REG)

# Make ln(Value_Added_per_emp)
INDUS_2550_VA_filtered <- INDUS_2550_VA_filtered %>% mutate(ln_Value_Added_per_emp = log(Value_Added_per_emp))

# Plot
ggplot(INDUS_2550_VA_filtered, aes(x = ln_Value_Added_per_emp, weight = WGT_REG,  group = REG, color = REG)) + geom_density(warnWbw = FALSE) + labs(title = "Distribution of value-added per employee (by region) in 2006", x = "ln(Value-added per employee)", y = "Density") + theme(legend.position = "bottom") + scale_color_manual(values = c("red", "blue", "green", "purple", "orange"), labels = c( "Bangkok", "Central", "North", "Northeast", "South")) + theme(legend.position = "bottom", legend.title = element_blank())

```

```{r}
# 2560
# Make REG as character
INDUS_2560_VA_filtered$REG <- as.character(INDUS_2560_VA_filtered$REG)

# Make ln(Value_Added_per_emp)
INDUS_2560_VA_filtered <- INDUS_2560_VA_filtered %>% mutate(ln_Value_Added_per_emp = log(Value_Added_per_emp))

# Plot
ggplot(INDUS_2560_VA_filtered, aes(x = ln_Value_Added_per_emp, weight = WGT,  group = REG, color = REG)) + geom_density(warnWbw = FALSE) + labs(title = "Distribution of value-added per employee (by region) in 2016", x = "ln(Value-added per employee)", y = "Density") + theme(legend.position = "bottom") + scale_color_manual(values = c("red", "blue", "green", "purple", "orange"), labels = c( "Bangkok", "Central", "North", "Northeast", "South")) + theme(legend.position = "bottom", legend.title = element_blank())

```

### Distribution of K/L (by region)

```{r}
# 2550
# Make REG as character
INDUS_2550_KL_filtered$REG <- as.character(INDUS_2550_KL_filtered$REG)

# Make ln(Capital_to_Labor)
INDUS_2550_KL_filtered <- INDUS_2550_KL_filtered %>% mutate(ln_Capital_to_Labor = log(Capital_to_Labor))

# Plot
ggplot(INDUS_2550_KL_filtered, aes(x = ln_Capital_to_Labor, weight = WGT_REG,  group = REG, color = REG)) + geom_density(warnWbw = FALSE) + labs(title = "Distribution of K/L (by region) in 2006", x = "ln(K/L)", y = "Density") + theme(legend.position = "bottom") + scale_color_manual(values = c("red", "blue", "green", "purple", "orange"), labels = c( "Bangkok", "Central", "North", "Northeast", "South")) + theme(legend.position = "bottom", legend.title = element_blank())

```

```{r}
# 2560
# Make REG as character
INDUS_2560_KL_filtered$REG <- as.character(INDUS_2560_KL_filtered$REG)

# Make ln(Capital_to_Labor)
INDUS_2560_KL_filtered <- INDUS_2560_KL_filtered %>% mutate(ln_Capital_to_Labor = log(Capital_to_Labor))

# Plot
ggplot(INDUS_2560_KL_filtered, aes(x = ln_Capital_to_Labor, weight = WGT,  group = REG, color = REG)) + geom_density(warnWbw = FALSE) + labs(title = "Distribution of K/L (by region) in 2016", x = "ln(K/L)", y = "Density") + theme(legend.position = "bottom") + scale_color_manual(values = c("red", "blue", "green", "purple", "orange"), labels = c( "Bangkok", "Central", "North", "Northeast", "South")) + theme(legend.position = "bottom", legend.title = element_blank())


```


# Analysis of firms with number of employees > 10 

## Pre-processing the data
### Filter the data >= 10 employees

```{r}
### First, replace NA with 0 in the number of employees
INDUS_2540 <- INDUS_2540 %>% mutate(A26 = ifelse(is.na(A26), 0, A26), A31 = ifelse(is.na(A31), 0, A31))

INDUS_2550 <- INDUS_2550 %>% mutate(A24 = ifelse(is.na(A24), 0, A24), A28 = ifelse(is.na(A28), 0, A28))

INDUS_2560 <- INDUS_2560 %>% mutate(B04 = ifelse(is.na(B04), 0, B04), B08 = ifelse(is.na(B08), 0, B08))

## Filter the data
INDUS_2540_atleast10 <- INDUS_2540 %>% filter(A26 + A31 >= 10)

INDUS_2550_atleast10 <- INDUS_2550 %>% filter(A24 + A28 >= 10)

INDUS_2560_atleast10 <- INDUS_2560 %>% filter(B04 + B08 >= 10)



```


