---
title: "Thesis_INDUS_Analysis"
format: html
execute:
  warning: false
---
## Explanation

In this document/code, I will examine key dimensions of manafacturing firms. The main goal is to see whether there are differences in key dimensions across different regions. The main characteristics that I will examine are:

1. Firm size (Number of employees)
  i) 2540: (A26 + A31)
  ii) 2550: (A24 + A28)
  iii) 2560: (B04 + B08)
2. Foreign Investment
  i) 2540: A05
  ii) 2550: A09
  iii) 2560: A09
3. Exporting
  i) 2540: A11
  ii) 2550: A15
  iii) 2560: A12
4. Sales
  i) 2540: F01
  ii) 2550: G01
  iii) 2560: D01
5. Profit before tax (Total income - Cost of sales - Administrative expenses - Costs of raw materials, production, goods, work done by others - wages bill)
  i) 2540: F09 - E01 - E02 - C01 - C02 - C03 - C04 - B04 - B08 - B09 - B10 - B11
  ii) 2550: G13 - E01 - E02 - C01 - C02 - C03 - C04 - B05 - B10
  iii) 2560: D13 - C21 - C41 - C06 - B19 - B24
6. Total Fixed Assets
  i) 2540: H07
  ii) 2550: I08
  iii) 2560:
7. Problems of operation
  i) 2540: H11_1, H11_2, H11_3
  ii) 2550: no info
  iii) 2560: J02, J03, J04, J05, J06, J07, J08, J09, J10, J11, J12, J13, J14, J15, J16, J17
8. Needs from the government
  i) 2560: J19, J20, J21, J22, J23, J24, J25, J26, J27, J28, J29, J30, J31, J32, J33, J34 
9. R&D Costs
  i) 2540: No info
  ii) 2550: E28
  iii) 2560: C32
10. Number of firms
  i) 2540: ??
  ii) 2550: sum of weights
  iii) 2560: sum of weights



## Import and Clean Data
```{r}
library(readxl)
library(dplyr)
library(ggplot2)
library(tidyr)
library(haven)
library(ggstats)

# Set working directory
setwd("D:/Onedrive-CEU/OneDrive - Central European University/CEU/Thesis/Thesis_code")

# Importing the data
INDUS_2540 <- read_sav("Data\\INDUS 2540 (1997)\\Microdata INDUS 2540\\Microdata INDUS 2540.sav")

INDUS_2550 <- read_sav("Data\\INDUS 2550 (2007)\\Microdata INDUS 2550\\Microdata INDUS 2550.sav")

INDUS_2560 <- read_sav("Data\\INDUS 2560 (2018)\\Microdata INDUS 2560\\Microdata INDUS 2560.sav")


```

## Pre-processing the data
### Divide weight by 10,000
```{r}
INDUS_2550 <- INDUS_2550 %>% mutate(WGT_CWT = WGT_CWT/10000, WGT_REG = WGT_REG/10000)

```

## Categorize number of employees (follow the same categorization as in year 2550)
1. 1
2. 2-3
3. 4-5
4. 6-10
5. 11-15
6. 16-20
7. 21-25
8. 26-30
9. 31-50
10. 51-100
11. 101-200
12. 201-500
13. 501-1000
14. > 1000

```{r}
## Categorized number of employees (2560)\
# 1 + NA should be 1
INDUS_2560 <- INDUS_2560 %>% mutate(B04 = ifelse(is.na(B04), 0, B04), B08 = ifelse(is.na(B08), 0, B08)) %>% mutate(SIZE_R = case_when(B04 + B08 == 1 ~ 1, B04 + B08 >= 2 & B04 + B08 <= 3 ~ 2, B04 + B08 >= 4 & B04 + B08 <= 5 ~ 3, B04 + B08 >= 6 & B04 + B08 <= 10 ~ 4, B04 + B08 >= 11 & B04 + B08 <= 15 ~ 5, B04 + B08 >= 16 & B04 + B08 <= 20 ~ 6, B04 + B08 >= 21 & B04 + B08 <= 25 ~ 7, B04 + B08 >= 26 & B04 + B08 <= 30 ~ 8, B04 + B08 >= 31 & B04 + B08 <= 50 ~ 9, B04 + B08 >= 51 & B04 + B08 <= 100 ~ 10, B04 + B08 >= 101 & B04 + B08 <= 200 ~ 11, B04 + B08 >= 201 & B04 + B08 <= 500 ~ 12, B04 + B08 >= 501 & B04 + B08 <= 1000 ~ 13, B04 + B08 > 1000 ~ 14))

```



```{r}
## Convert SIZE_R to factor
INDUS_2550 <- INDUS_2550 %>% mutate(SIZE_R = factor(SIZE_R, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14), labels = c("1", "2-3", "4-5", "6-10", "11-15", "16-20", "21-25", "26-30", "31-50", "51-100", "101-200", "201-500", "501-1000", ">1000")))

INDUS_2560 <- INDUS_2560 %>% mutate(SIZE_R = factor(SIZE_R, levels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14), labels = c("1", "2-3", "4-5", "6-10", "11-15", "16-20", "21-25", "26-30", "31-50", "51-100", "101-200", "201-500", "501-1000", ">1000")))


```



## Tabulating the data
### Firm Size (by region)

```{r}
### Calculate the average number of employees by region
# 2550
Avg_emp_2550 <- INDUS_2550 %>% mutate(A24 = ifelse(is.na(A24), 0, A24), A28 = ifelse(is.na(A28), 0, A28)) %>% group_by(REG) %>% summarise(Avg_emp_50 = weighted.mean(A24 + A28, WGT_REG, na.rm = TRUE))

# 2560
Avg_emp_2560 <- INDUS_2560 %>% mutate(B04 = ifelse(is.na(B04), 0, B04), B08 = ifelse(is.na(B08), 0, B08)) %>% group_by(REG) %>% summarise(Avg_emp_60 = weighted.mean(B04 + B08, WGT, na.rm = TRUE))

```

### Number of firms (by region)

```{r}
# 2550
Num_firms_2550 <- INDUS_2550 %>% group_by(REG) %>% summarise(Num_firms_50 = sum(WGT_REG, na.rm = TRUE))

# 2560
Num_firms_2560 <- INDUS_2560 %>% group_by(REG) %>% summarise(Num_firms_60 = sum(WGT, na.rm = TRUE))
```



## Plotting the data
### Distribution of Firm Size (by region)

```{r}
# 2550
ggplot(INDUS_2550 %>% drop_na(SIZE_R)) + aes(x = SIZE_R, weight = WGT_REG, y = after_stat(prop)) + geom_bar(stat = "prop") + facet_wrap(~REG, ncol = 1) + labs(title = "Distribution of Firm Size (by region)", x = "Number of Employees", y = "Proportion")
```

```{r}

# 2560
ggplot(INDUS_2560 %>% drop_na(SIZE_R)) + aes(x = SIZE_R, weight = WGT, y = after_stat(prop)) + geom_bar(stat = "prop") + facet_wrap(~REG, ncol = 1) + labs(title = "Distribution of Firm Size (by region)", x = "Number of Employees", y = "Proportion")


```

```{r}
## Overlay the two graphs
Dist_overlay <- ggplot(NULL, aes(x = SIZE_R, y = after_stat(prop))) + geom_bar(data = INDUS_2550 %>% drop_na(SIZE_R), aes(weight = WGT_REG, fill = "2550"), stat = "prop", alpha = 0.4) + geom_bar(data = INDUS_2560 %>% drop_na(SIZE_R), aes(weight = WGT, fill = "2560"), stat = "prop", alpha = 0.4) + facet_wrap(~REG, ncol = 1) + labs(title = "Distribution of Firm Size (by region)", x = "Number of Employees", y = "Proportion") + labs(fill = "Year") + theme(legend.position = "bottom")

Dist_overlay


```

